### 2020-03-07 draft_ABP.tex
merge from overleaf
update sec 1.1

Another example still comes from a hyperplane arrangement, the Shi arrangement,
which is also $B_n$ type cluster stringy integral.
The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom of global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
given by the following hyperplains
\[
    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
\]
for $1\leq i<j\leq n+1$. Its stringy integral is
\[
	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
\]
(Zhenjie: Carefully check the notation!)
The $u$-variables of this configuration space are
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.

(u eq of $B_n$)

@@

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
Each facet of $\mathscr P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, 
whose equation is 
\begin{equation}\label{Pnfacet}
	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
\end{equation}
so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
can be solved from above equations:
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.

>>>>

Another example still comes from a hyperplane arrangement, the Shi arrangement,
which is also $B_n$ type cluster stringy integral.
The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom of global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. The Shi arrangement is 
given by the following hyperplains
\[
	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
\]
and its stringy integral is 
\[
\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
\]
where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
The $u$-variables of this configuration space are
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.
They satisfy the following $u$-equations 
\begin{align*}	
1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk}.
\end{align*}

@@

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
Each facet of $\mathscr P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, 
whose equation is 
\begin{equation}\label{Pnfacet}
	F_I:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
\end{equation}
so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
can be solved from above equations:
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.
